Characterizing breast cancer cells

### 2022-12-05 austins_analysis.rmd
updated powerpoint

Random Forrest
```{r}
#Random Forrest
random_forrest <- train(diagnosis ~ ., data = training, method = "ranger", metric="ROC", trControl = train_control, preProcess=c("center", "scale"))
rf_pred <- predict(random_forrest, test)
rf_confusion <- confusionMatrix(rf_pred, test$diagnosis, positive = "M")
print(rf_confusion)
```

KNN
```{r}
#KNN
knn <- train(diagnosis ~ ., data = training, method = "knn", metric="ROC", trControl = train_control)
knn_pred <- predict(knn, test)
knn_confusion <- confusionMatrix(knn_pred, test$diagnosis, positive = "M")
print(knn_confusion)
```

Radial Support Vector Machine
```{r}
#Radial Support Vector Machine
svm <- train(diagnosis ~ ., data = training, method = "svmRadial", trControl = train_control, metric="ROC")
svm_pred <- predict(svm, test)
svm_confusion <- confusionMatrix(svm_pred, test$diagnosis, positive="M")
print(svm_confusion)
```

```{r}
#Logistic Regression
logistic <- train(diagnosis ~ ., data = training, method = "glm", trControl = train_control, metric="ROC")
logistic_pred <- predict(logistic, test)
logistic_confusion <- confusionMatrix(logistic_pred, test$diagnosis, positive="M")
print(logistic_confusion)
logistic$finalModel
ggplot(varImp(logistic))
imp <- varImp(logistic)
top10 <- rownames(data.frame(imp[1]))[1:10]
```

```{r}
logistic2 <- train(diagnosis ~ top10, data = training, method = "glm", trControl = train_control, metric="ROC")

>>>>

Random Forrest
```{r}
#Random Forrest
random_forrest <- train(diagnosis ~ ., data = training, method = "ranger", metric="ROC", trControl = train_control, preProcess=c("center", "scale"))
rf_pred <- predict(random_forrest, test)
rf_confusion <- confusionMatrix(rf_pred, test$diagnosis, positive = "M")
print(rf_confusion)

KNN
```{r}
#KNN
knn <- train(diagnosis ~ ., data = training, method = "knn", metric="ROC", trControl = train_control)
knn_pred <- predict(knn, test)
knn_confusion <- confusionMatrix(knn_pred, test$diagnosis, positive = "M")
print(knn_confusion)
ggplot(varImp(knn))
varsKNN <- rownames(data.frame(varImp(knn)[1]))[1:10]
```
```

Radial Support Vector Machine
```{r}
#Radial Support Vector Machine
svm <- train(diagnosis ~ ., data = training, method = "svmRadial", trControl = train_control, metric="ROC")
svm_pred <- predict(svm, test)
svm_confusion <- confusionMatrix(svm_pred, test$diagnosis, positive="M")
print(svm_confusion)
ggplot(varImp(svm))
varsSVM <- rownames(data.frame(varImp(svm)[1]))[1:10]
```

```{r}
#Logistic Regression
logistic <- train(diagnosis ~ ., data = training, method = "glm", trControl = train_control, metric="ROC")
logistic_pred <- predict(logistic, test)
logistic_confusion <- confusionMatrix(logistic_pred, test$diagnosis, positive="M")
print(logistic_confusion)
logistic$finalModel
ggplot(varImp(logistic))
varsLOGISTIC <- rownames(data.frame(varImp(logistic)[1]))[1:10]
```

```{r}
logistic2 <- train(diagnosis ~ area_mean + area_worst + concave.points_mean + texture_mean + radius_worst + concavity_se + fractal_dimension_se, data = training, method = "glm", trControl = train_control, metric="ROC")
logistic2_pred <- predict(logistic2, test)
logistic2_confusion <- confusionMatrix(logistic2_pred, test$diagnosis, positive="M")
print(logistic2_confusion)
```

```{r}

### 2022-12-05 powerpoint.rmd
updated powerpoint

```{r, echo=FALSE}
#histogram
print(ggplot(data, aes(x = diagnosis)) + geom_bar(aes(fill=diagnosis)) + labs(title = "Histogram of Diagnosis", x = "Diagnosis", y = "Count", fill="Diagnosis"))
```

## Plot
```{r, echo=FALSE}
#scatterplot
print(ggplot(data, aes(x = radius_mean, y = texture_mean, color = diagnosis)) + geom_point() + 
    labs(title = "Scatterplot of Radius Mean vs Texture Mean", x = "Radius Mean", y = "Texture Mean", color="Diagnosis"))
```

>>>>

# Exploratory Data Analysis

# Model Building

# Testing Accuracy
